CYO Project Report - Brazilian Ecommerce

### 2021-07-11 finalReport.Rmd
updated code and tested for random forest with seller_id changes

```{r knn model, echo = FALSE}
#TODO can be removed
set.seed(seed=1,sample.kind = 'Rounding')

tuningControl=trainControl(method = "cv", number = 3, p = .8)
knn_fit <- train(number_of_hours~., train_subset, method='knn',tuneGrid=data.frame(k=c(27,34,41)),trControl=tuningControl)

predictions <- predict(knn_fit,test_subset %>% select(-number_of_hours))

RMSE(predictions,(test_subset %>% pull(number_of_hours) ))
#199.448 for k=34

@@

RMSE(predictions,(test_subset %>% pull(number_of_hours) ))
# 184.1709 for mtry 15. Technically there are total of 79 variables due to 73 product categories and 6 other predictors

>>>>

@@

RMSE(predictions,(test_subset %>% pull(number_of_hours) ))
# 184.5549 for mtry 15. Technically there are total of 79 variables due to 73 product categories and 6 other predictors
